Average solar wind and geomagnetic activity influence on the equatorial plasma mass density at geosynchronous orbit

### 2016-07-28 paper/paper.tex
Making sure figures still valid. Adding ability to make presentation figures

Our first analysis uses GOES-6 data only from the time interval 1989-1991, which corresponds with the interval used in the epoch analysis of \cite{Takahashi2010}. In this interval, there were 75 $D_{st}$ events where $D_{st}$ remained below the $-50$~nT threshold for at least 12 hours.  For both types of events, the first hour of a local minimum $D_{st}$ following a threshold crossing defines the zero epoch time, and for each event, $4\cdot24$ hours were considered before and $8\cdot24$ hours after event onset.  To compute the epoch averages on a daily time scale, the median value of all available measurements for all events centered on a window of $\pm 12$ hours of the epoch zero hour was computed, and these averaging windows were shifted in increments of $24$~hours. Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians for each event in 1-day bins and then compute the medians across events on each epoch day.

The stack plot in the upper panel of Figure \ref{DailyAveragedDstEvents} shows the epoch averages for the 75 events from 1989-1991.  The minimum $D_{st}$ median is $-75$~nT.  Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$ before and after the event, although the magnitude of increase observed here is $7$ amu/cm$^3$ (from 18 to 25~amu/cm$^3$) instead of the increase of $\sim 10$ amu/cm$^3$ found in Figure 11 of \cite{Takahashi2010}.  The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute the medians and red error lines.  Error lines for each parameter are the standard deviation of the values used in computing the median divided by the square root of the number of values. For the non-$\rho_{eq}$\ parameters, the number of measurements used in computing the medians is typically equal to the number of events, which is much larger than the number of $\rho_{eq}$\ values as all available measurements were used instead of restricting to only values where a $\rho_{eq}$ value also existed.

@@

If a statistically significant difference in the medians between two days existed, the fraction of bootstrap samples with a different sign is expected to be much smaller ($<$ 5\%).  In terms of a hypothesis test, we cannot reject the null hypothesis that the medians are the same with a confidence higher than 100 minus the \% value shown in the table; the highest confidence level of 87.8\% is in the difference between day 0 and day -1.

These tests indicate that there is not a statistically significant difference in medians of $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.  In addition, the observed differences are on the order of only 25\% of the value of $\rho_{eq}$ on the onset day, which is similar to the variation in the observations over the displayed epoch time interval.

@@

We have also considered hourly averages as shown in the top panel of Figure~\ref{HourlyAveragedDstEvents}.  A total of 668 $D_{st}$ events were found in the interval of May 1983 through August 1991 with an average duration of 9 hours and a median duration of 3 hours.    In this plot, the overall trend is similar to that found in the bottom panel of Figure~\ref{HourlyAveragedDstEvents} - $\rho_{eq}$ is slightly elevated at the time of the threshold crossing of $D_{st}$ with respect to the values one day before and after, but the elevation is small relative to the error bars around the time of the event onset.

>>>>

Our first analysis uses GOES-6 data only from the time interval 1989-1991, which corresponds with the interval used in the epoch analysis of \cite{Takahashi2010}. In this interval, there were 75 $D_{st}$ events where $D_{st}$ remained below the $-50$~nT threshold for at least 12 hours.  For both types of events, the first hour of a local minimum $D_{st}$ following a threshold crossing defines the zero epoch time, and for each event, $4\cdot24$ hours were considered before and $8\cdot24$ hours after event onset. For multiple detected threshold crossings within 24 hours of each other, the first crossing was selected as the event since visual inspection showed the following crossings to typically be from brief deviations during the recovery period. To compute the epoch averages on a daily time scale, the median value of all available measurements for all events centered on a window of $\pm 12$ hours of the epoch zero hour was computed, and these averaging windows were shifted in increments of $24$~hours. Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians for each event in 1-day bins and then compute the medians across events on each epoch day.

The stack plot in the upper panel of Figure \ref{DailyAveragedDstEvents} shows the epoch averages for the 75 events from 1989-1991.  The minimum $D_{st}$ median is $-75$~nT.  Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$ before and after the event, although the magnitude of increase observed here is, on average, $4.5$ amu/cm$^3$ (from $\sim$19 to ${\sim}$24~amu/cm$^3$) instead of the increase of ${\sim} 10$ amu/cm$^3$ found in Figure 11 of \cite{Takahashi2010}.  The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute the medians and red error lines.  Error lines for each parameter are the standard deviation of the values used in computing the median divided by the square root of the number of values. For the non-$\rho_{eq}$\ parameters, the number of measurements used in computing the medians is typically equal to the number of events, which is much larger than the number of $\rho_{eq}$\ values as all available measurements were used instead of restricting to only values where a $\rho_{eq}$ value also existed.

@@

If a statistically significant difference in the medians between two days existed, the fraction of bootstrap samples with a different sign is expected to be much smaller ($<$ 5\%).  In terms of a hypothesis test, we cannot reject the null hypothesis that the medians are the same with a confidence higher than 100 minus the \% value shown in the table; the highest confidence level of 89\% is in the difference between day 0 and day -1.

These tests indicate that there is not a statistically significant difference in medians of $\rho_{eq}$ on the day before and day after a threshold crossing in $D_{st}$.  In addition, the observed differences are on the order of only 20\% of the value of $\rho_{eq}$ on the onset day, which is similar to the variation in the observations over the displayed epoch time interval.

@@

We have also considered hourly averages as shown in the top panel of Figure~\ref{HourlyAveragedDstEvents}.  A total of 333 $D_{st}$ events were found in the interval of May 1983 through August 1991 with an average duration of 10 hours and a median duration of 3 hours. In this plot, the overall trend is similar to that found in the bottom panel of Figure~\ref{HourlyAveragedDstEvents} - $\rho_{eq}$ is slightly elevated at the time of the threshold crossing of $D_{st}$ with respect to the values one day before and after, but the elevation is small relative to the error bars around the time of the event onset.
